---
title: "INFO550_Homework2"
author: "Jordan Ahn"
date: "9/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Examining the Statistical Capacity of countries

This report will briefly explore the potential relationship between a country's capacity for analyzing and reporting data using statistical methods and a few important health indicators such as life expectancy, under 5 mortality, and maternal mortality. With sufficient data, current COVID-19 data might also be assessed.

```{r data, echo = FALSE}
statcap <- read.csv("/Users/Jordan/Desktop/statistical-capacity-indicator.csv")

names(statcap) <- c('country', 'countrycode','year','statcapindicator')

```

### Statistical Capacity by region from 2004-2017

```{r graphs, echo=FALSE}
westafrica <- c('Senegal', 'Guinea', 'Sierra Leone', 'Benin', 'Togo', 'Gambia')
wa_subset <- statcap %>% 
            filter(country %in% westafrica)

ggplot(data = wa_subset, aes(x = year, y = statcapindicator, colour = country)) +
  geom_line() +
  geom_point() +
  ggtitle("Statistical Capacity of West African Countries (2004-2017)") +
  xlab("Year") +
  ylab("Statistical Capacity Indicator") +
  labs(colour = "Country")
```


